Interpersonal Accuracy of Thoughts, Affect, and Personality Traits

### 2022-05-19 manuscript.Rmd
select variables and fix the title

---
title: "Target Readability in Interpersonal Accuracy"
author: "Murat Kezer"
output: 
    html_document:
      theme: cerulean
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 2
      code_folding: hide
---

@@

rm(list = gdata::keep(df))
```

>>>>

---
title: "Interpersonal Accuracy of Thoughts, Affect, and Personality Traits"
author: "Murat Kezer"
output: 
    html_document:
      theme: cerulean
      code_download: TRUE
      toc: TRUE
      toc_float:
        collapsed: FALSE
      toc_depth: 2
      code_folding: hide
---

@@

rm(list = gdata::keep(df))

# select relevant variables
df <- df %>% 
  select(
    PerUn:Group, # id variables
    EA100, # emphatic accuracy (EA) for thoughts out of 100
    sex:race_text, # demographic variables
    strait1:strait26, # perceivers' self-reported personality traits
    imp1:imp16, # rapport during the interaction
    ptrait1:ptrait26, # perception of targets' personality traits
    targSR1:targSR26, # targets' self-reported personality traits
    Self1:Self120, # perceivers' self-reported continuous affect
    Part1:Part120, # perception of targets'continuous affect
    TargSR1:TargSR120, # targets' self-reported continuous affect
    as1:as13, # attachment styles
    auth1:auth12rc, # authenticity
    mask1:mask13, # masking
    ntb1:ntb10, # need to belong
    ucla1:ucla20rc, # ucla loneliness scale
    fne1:fne12, # fear of negative evaluation
    beq1:beq16, # berkeley expressivity questionnaire
    erq1:erq10, # emotion regulation (expressive suppression)
    rse1:rse10rc, # rosenberg self-esteem
    sat1:sat5, # satistaction with life
    pow1:pow8, # sense of power
    sias1:sias12, # social interaction anxiety scale
    InsecAtt:SIAPSc, # composite variables
    InformantTot, # number of informants for targets
    strait4rc:strait25rc, # perceivers' traits reversed and centered
    Extr:Trust, # composite variables for personality traits
    itrait1:itrait26, # informant reports of targets' personality traits
    per_InsecAtt_INFmeanC:per_Trust_INFmeanC # informant reports 
  ) %>% 
  arrange(PerUn, TarUn, DyUn, Group)

# rename variables for a final time
